
# R plot gallery

#### Contents {-}
+ [Multiple 95% Confidence Intervals](#multiple-95-confidence-intervals)
+ [Pirate Plot](#pirate-plot)
+ [Beeswarm Plot](#beeswarm-plot)
+ [Bar Plot](#bar-plot)
+ [Calender](#calendar)
+ [Correlation Plot](#correlation-plot)
+ [Table Visualization](#table-visualization)
+ [Heatmap](#heatmap)
+ [Compare Two Group Means](#compare-two-group-means)

#### Multiple 95% Confidence Intervals {-}
```{r}
data.frame(value = rnorm(12, mean = 0, sd = 0.05)) %>% 
  mutate(lower = value - runif(12, 0, 0.4), 
         upper = value + runif(12, 0, 0.4), 
         REG = rep(c("A", "B", "C", "D"), 3), 
         est = mean(value), 
         index = rep(1:3, each = 4)) %>% 
  ggplot(aes(x = lower, xend = upper, 
             y = index + rep((0:(length(unique(REG))-1))/10, 3), 
             yend = index + rep((0:(length(unique(REG))-1))/10, 3), 
             color = REG)) + 
  geom_segment(lwd = 1, alpha = 0.5) + 
  scale_color_brewer(palette = "Set1") + 
  labs(y = "", x = "Reduction Rate") + 
  scale_y_continuous(breaks = 1:3, 
                     labels = c("method 1", "method 2", "method 3")) + 
  geom_segment(aes(x = est, xend = est, 
                   y = index - 0.1, 
                   yend = index + (length(unique(REG)))/10)) + 
  geom_point(aes(x = value, 
                 y = index + rep((0:(length(unique(REG))-1))/10,  3))) + 
  theme_bw() + 
  ggtitle("Reduction Rate of Treatment Compared With Placebo") + 
  theme(plot.title = element_text(hjust = 0.5), 
        text= element_text(size = 15))
```

#### Pirate Plot {-}
```{r}
require(yarrr)

yarrr::pirateplot(weight ~ Diet, 
           data = ChickWeight, 
           main = "Pirate plot", 
           inf.method = "ci", 
           theme = 2,   # change theme, from 1 to 4
           pal = "decision", # use piratepal(palette = "all") to check available palettes 
           bar.f.o = 0.2)
```

#### Beeswarm plot {-}
```{r}
require(ggbeeswarm)

ggplot(iris, aes(Species, Sepal.Length, colour = Species)) +
  geom_violin(width = 0.5) +
  geom_beeswarm() +
  theme_classic() +
  scale_color_brewer(palette = "Set1")
```

#### Bar Plot {-}
```{r}
dat2 <- data.frame(
  categ = rep(c("Roads", "Canals", "Early railways", "Railways"), each = 3) %>% fct_inorder(), 
  group =  rep(c("Maximum", "Mean", "Minimum"), 4), 
  fill = as.character(c(1,1,1,1,1,1, 2, 1, 3, 1,1,1)), 
  pattern = c(rep("N", 6), "D", rep("N", 5)), 
  record = c(NA, 5, NA, 11.5, 3.77, 1.4, 14.3, 6, 2.3, NA, 1.4, NA)
)


dat2 %>% dplyr::filter(is.na(record) == FALSE) %>% 
ggplot() + 
  geom_bar_pattern(aes(x = categ, y = record, fill = fill, group = group, pattern = pattern), 
                   width=0.4, position = position_dodge2(width=0.5, preserve = "single"), 
                   color = "black", 
                   stat = "identity", 
                  pattern_density = 1.0,
                  pattern_fill = 'grey',
                  pattern_key_scale_factor = 0.5) + 
  scale_fill_manual(values = c("#1B4264","#D3CEC7","#5A6065"), 
                    labels = c("Mean", "Maximum", "Minimum")) +
  scale_pattern_manual(values = c(D = "stripe", N = "none"), guide = "none") + 
  guides(fill = guide_legend(override.aes = list(pattern = "none"), 
                             title = NULL)) + 
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14)) + 
  labs(x = NULL, y = "Pence") + 
  theme_bw() + 
  theme(text = element_text(size = 15), axis.text.y = element_text(angle = 30, hjust = 1)) 
```


#### Calendar {-}
```{r}
require(sugrrants)
require(lubridate)

data.frame(date = lubridate::ymd(strtrim(seq(ISOdate(2017,10,1), ISOdate(2018,2,28), "DSTday"),10)), 
           # or as.Date("2017-10-1") + 0:150
           n = sample(1:100, size = 151, replace = T)) %>% 
  sugrrants::frame_calendar(x = 1, y = 1, date = date) %>% 
  ggplot(aes(x = .x, y = .y)) +
  ggtitle("Daily sold units") +
  theme_bw() + 
  theme(legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5)) +
  geom_tile(aes(x = .x+(1/13)/2, y = .y+(1/9)/2, fill = n), colour = "grey50") +
  scale_fill_distiller(name = "", palette = "RdYlBu") -> p2.sale 
  sugrrants::prettify(p2.sale, label = c("label", "text", "text2")) # label: month and year; text: weekday at the bottom; text2: day of month
```


#### Correlation Plot {-}
```{r}
require(corrplot)

cor(mtcars) %>% 
  corrplot::corrplot(., type = "upper", order = "hclust")
```

#### Table Visualization {-}
```{r fig.width=8}
require(formattable)
require(DT)

df <- 
  data.frame(id = 1:10,  
             name = c("Bob", "Ashley", "James", "David", "Jenny",
                      "Hans", "Leo", "John", "Emily", "Lee"),   
             age = c(28, 27, 30, 28, 29, 29, 27, 27, 31, 30),  
             grade = c("C", "A", "A", "C", "B", "B", "B", "A", "C", "C"),  
             test1_score = c(8.9, 9.5, 9.6, 8.9, 9.1, 9.3, 9.3, 9.9, 8.5, 8.6),
             test2_score = c(9.1, 9.1, 9.2, 9.1, 8.9, 8.5, 9.2, 9.3, 9.1, 8.8),  
             final_score = c(9, 9.3, 9.4, 9, 9, 8.9, 9.25, 9.6, 8.8, 8.7),  
             registered = c(TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE),
             stringsAsFactors = FALSE)

formattable(df, 
            list(age = color_tile("white", "orange"),
                 grade = formatter("span", 
                                   style = x ~ ifelse(x == "A", style(color = "green", font.weight = "bold"), NA) ),    
                 area(col = c(test1_score, test2_score)) ~ normalize_bar("pink", 0.4),              
                 final_score = formatter("span",  style = x ~ style(color = ifelse(rank(-x) <= 3, "green", "gray")),
                                         x ~ sprintf("%.2f (rank: %02d)", x, rank(-x))),
                 registered = formatter("span", style = x ~ style(color = ifelse(x, "green", "red")),
                                        x ~ icontext(ifelse(x, "ok", "remove"), ifelse(x, "Yes","No")))
                 )
            )
```


#### Heatmap {-}
```{r}
ggplot(airquality, aes(Day, Month, fill = Temp)) + 
  geom_tile() + 
  scale_x_continuous(breaks = seq(1:31)) + 
  theme_bw() + 
  scale_fill_viridis_c(option = "A") 
```

```{r}
# Example 2
set.seed(1234)
mydata <- matrix(rnorm(5*10), ncol = 10)
colnames(mydata) <- letters[1:10] 
heatmap(mydata, 
        # Colv = NA, # Rowv = NA,   # hide the clustering 
        main = "heatmap", col = cm.colors(256))
```

#### Compare Two Group Means {-}
```{r}

require(dabestr)

mydata <- iris[iris$Species %in% c("setosa", "versicolor"), ] %>% 
  mutate(Class = ifelse(Sepal.Length > 5.5, "Long", "Short"))

mytest <- dabest(mydata, Species, Petal.Width,    # Compare Petal.Width for Species
                 idx = c("setosa", "versicolor"), # setosa is the control group 
                 paired = FALSE) 

mymean_diff <- mean_diff(mytest)

plot(mymean_diff, color.column = Class)
```


